---
title: "Homework 1 (CSC 495)"
author: "Kai Chung, Ying"
date: "Winter 2017"
output: html_document
---
## Some visualizations of the Dining data

```{r}
library(knitr)
setwd('/Users/KevQuant/Desktop/Depaul/csc495/wk1/hwk1')

read_chunk("hwk1.R")
knitr::opts_chunk$set(echo = TRUE)
```

### Load packages

```{r C1, results="hide", warning=FALSE, message=FALSE}
```


### Load the necessary libraries and data

Note that I include the chunk options results="hide", etc. because
loading libraries produces a lot of output that we don't want
on our page. You will need to install all of these packages for
this part to work. 

```{r C1, results="hide", warning=FALSE, message=FALSE}

```

### Loading the data

Next we need to load the data file. This file is included in the homework zip file. You will need to set the path appropriately. 

```{r C2}

```

### Pointers to help

You will find it useful to refer to the following help articles in doing this assignment.

* igraph-vs-attributes
* igraph-es-attributes
* igraph.plotting
* degree
* graph.strength

## Graded portion *(14 points + 2 extra credit)*

### Step 1: Introduction *(1 pt)*

* Go to Slack. Upload an actual picture of yourself as a profile picture. (Not your dog or your favorite Pokemon.) Thanks.
* Post to the "#introductions" topic:
    + Your name
    + Your degree program
    + What types of networks you are interested in
* Post to the "#smallworldstory" topic:
    + A "small world" story: a situation in which an unexpected social connection manifested itself.

### Step 2: Names *(1 pt)*

Get the names of the students from the nodes in the dining network.

```{r C3}
```

### Step 3: Visualization 1 *(2 pts)*

Create a simple, but not ugly visualization of the dining network using base plotting in igraph (`plot`). It should include the names for each vertex and
arrows indicating the direction of the network. 

```{r C4, fig.width=7, fig.height=6}

```

### Step 4: Calculate in-degree *(2 pts)*

Calculate in-degree for the nodes (`degree` function with `mode="in"`) and display a summary (`summary` function) of the in-degree data.  (Hint: The mean should be 2 and the max should be 6.)

```{r C5}

```

### Step 5: Visualization 2 *(2 pts)*

Plot the in-degree distribution in a histogram. You can use either
base plotting or ggplot to do this.

```{r C6, fig.width=4, fig.height=3}

```

```{r C7, fig.width=4, fig.height=3}

```

### Step 7: Computing edge weights *(1 pt)*

Next we will add appropriate edge weights to our calculations. There are weights on the edges, but they are the values 1 and 2, representing first and second choice. The value 1 should be a **stronger** tie and the value 2 a **weaker** one. 

Create a new edge attribute `wt` that is 1 when the `weight` attribute is 1 and 0.5 when the `weight` attribute is 2. You can use `ifelse` or arithmetic calculation to do this.

```{r C8}

```

### Step 8: Compute weighted degree *(1 pt)*

The `graph.strength` function computes weighted degree values. Use this function to compute weighted in-degree using the `wt` attribute computed in Step 7.

(Hint: the summary should show a mean of 1.5 and a max of 5.)

```{r C9}

```

### Step 9: Visualization 4 *(2 pts)*
Weighted degree will be a real number, not an integer. Use a binwidth of 0.5 and make sure that the limits on X axis are correct.

```{r C10, fig.width=4, fig.height=3}

```

### Extra credit: Weighted plot *(2 pts)*

Produce a graph plot in which the nodes are sized as a function
of weighted in-degree. (Use the `size` parameter to the `plot` function.) The label should also be sized by weighted degree. (The `label.cex` parameter does this.) Edge width should be function of the edge weight, using the `edge.width` parameter.

Note that you are striving for readability in the visualization.
Some nodes have in-degree of zero -- it is not a good idea for these to have zero size vertices and labels. You will need to compute a function of the in-degree value to get appropriate sizes and this function will be different for node size and label size.

A sample visualization is included in the zip file for inspiration.

```{r Extra, fig.width=7, fig.height=6}


```

